Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-05-10 WholePlotTrajectories.Rmd
figures formatting

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2 3
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Cirad, Univ montpellier, UR Forests & Societies.
    address: >
      Montpellier,
      France.
  - affsuperscript: 3
    dptuniv: INPHB, Institut National Polytechnique Félix Houphouet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

@@

@@

```{r DivTaxo, out.width = '100%', fig.asp = 1.5/3, echo=FALSE,fig.cap="Trajectories of the difference to the 1989 inventories (5 years after disturbance) over 30 years after disturbance of plots communities (ref:Bolda) Richness, (ref:Boldb) Shannon and (ref:Boldc) Simpson diversities. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/ReplacementTraj_ForGraphs")

@@

```{r DivFun, out.width = '100%', echo=FALSE, fig.cap="Upper panels, Trajectories of the Simpson taxonomic diversity and Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3. Lower panels, Relationship between the initial %AGB removed and the values of Simpson (c) and Rao (d) diversities at three times after disturbance. Solid lines colors represent the time, 10 years (yellow), 20 years (orange) and 30 years (brown) after disturbance.", fig.env="figure"}
load("DB/SimpsonDraw");load("DB/FunctionalTraj_ForGraphs")
load("DB/SimpsonIDH");load("DB/RaoIDH");load("DB/LostAGB")

@@

@@

RedundancyPlot(RedundancyTraj)
mtext("Functional Redundancy",side=3,adj=0,line=1.5)
mtext("Sum of abundance-weighted Trait Probability Density",side=3,adj=0,cex=0.8,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1)

>>>>

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Eric Marcon
    authsuperscript: 1
  - name: Bruno Hérault
    authsuperscript: 2 3
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: Cirad, Univ montpellier, UR Forests & Societies.
    address: >
      Montpellier,
      France.
  - affsuperscript: 3
    dptuniv: INPHB, Institut National Polytechnique Félix Houphouet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: http://www.ecofog.gf/spip.php?article47
abstract: >   #Pour avoir plusieurs lignes qui suivent. Commencer à 2 caractères
  Résumé de l'article.
keywords: [mot-clés, séparés par des virgules]
journalinfo: Hal xxx
archive: DOI xxxx
date: "`r format(Sys.time(), '%d %B %Y')`"
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::gitbook: default
  bookdown::word_document2: default
---

@@

(ref:Boldd) **(d)**

@@

```{r DivTaxo, out.width = '100%', fig.asp = 1.5/3, echo=FALSE, fig.cap="Trajectories of the difference to the 1989 inventories (5 years after disturbance) over 30 years after disturbance of plots communities (ref:Bolda) Richness, (ref:Boldb) Shannon and (ref:Boldc) Simpson diversities. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3.", fig.env="figure*"}
load("DB/ReplacementTraj_ForGraphs")

@@

```{r IDHplot,  echo=FALSE, fig.cap="Upper panels, Trajectories of the Simpson taxonomic diversity (ref:Bolda) and Rao functional diversity (ref:Boldb) over 30 years after disturbance, corresponding to the median and 0.025 and 0.975 percentile observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3. Lower panels, Relationship between the initial \\%AGB removed and the values of Simpson (ref:Boldc) and Rao (ref:Boldd) diversities at three times after disturbance. Solid lines colors represent the time, 10 years (yellow), 20 years (orange) and 30 years (brown) after disturbance.", fig.env="figure*"}

load("DB/SimpsonDraw");load("DB/FunctionalTraj_ForGraphs")
load("DB/SimpsonIDH");load("DB/RaoIDH");load("DB/LostAGB")

@@

The functional redundancy was measured as the sum of weighted overlap among species in the communities.
Species functional space were defined in the main two-dimensional space of a PCA analysis based on all leaf and stem and maximum height traits (see appendix I for more details). 
Plots functoinal redundancy was followed in comparison to their initial value right after logging so that only communities dynamics are followed apart from the impact of logging itself.
While the functional redundancy of control plots remained stable along the 30 years it systematically decreased after disturbance (\@ref(fig:RedFun)).
The decrease of functional redundancy was comparable between all disturbed plots but started later for the most disturbed plots.
Plots recovery did not seemed correlated to the initial disturbance, for five out of nine disturbed plots the initial functional redundancy was had recovered while it was still decreasing or stabilized at lower values for the fou other plots.

@@

par(mar=c(5,4,5,2))
RedundancyPlot(RedundancyTraj)
mtext("Functional Redundancy",side=3,adj=0,line=1.5)
mtext("Sum of abundance-weighted Trait Probability Density",side=3,adj=0,cex=0.8,line=0.5)
mtext("Years since disturbance",side=1,line=2.2,adj=1)

### 2018-05-10 WholePlotTrajectories.tex
figures formatting

% User-adder preamble
\usepackage{textcomp} \DeclareUnicodeCharacter{B0}{\textdegree}
\usepackage{tabu}
\renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
\hyphenation{bio-di-ver-si-ty sap-lings}

@@

\textbackslash{}begin\{figure\}

\{\centering \includegraphics[width=1\linewidth]{WholePlotTrajectories_files/figure-latex/DivFun-1}

\}

\textbackslash{}caption\{Upper panels, Trajectories of the Simpson
taxonomic diversity and Rao functional diversity over 30 years after
disturbance. Trajectories correspond to the median (solid line) and
0.025 and 0.975 percentile (gray envelope) observed after 50 iteration
of the taxonomic uncertainty propagation and the missing trait value
filling processes. Initial treatments are represented by solid lines
colors with green for control, blue for T1,orange for T2 and red for T3.
Lower panels, Relationship between the initial \%AGB removed and the
values of Simpson (c) and Rao (d) diversities at three times after
disturbance. Solid lines colors represent the time, 10 years (yellow),
20 years (orange) and 30 years (brown) after
disturbance.\}\label{fig:DivFun} \textbackslash{}end\{figure\}

>>>>

% User-adder preamble
\usepackage{textcomp} \DeclareUnicodeCharacter{B0}{\textdegree}
\usepackage{tabu} \usepackage{caption}
\captionsetup{justification = justified}
\renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
\hyphenation{bio-di-ver-si-ty sap-lings}

@@

{\centering \includegraphics{WholePlotTrajectories_files/figure-latex/IDHplot-1}

\caption{Upper panels, Trajectories of the Simpson taxonomic diversity \textbf{(a)} and Rao functional diversity \textbf{(b)} over 30 years after disturbance, corresponding to the median and 0.025 and 0.975 percentile observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3. Lower panels, Relationship between the initial \%AGB removed and the values of Simpson \textbf{(c)} and Rao \textbf{(d)} diversities at three times after disturbance. Solid lines colors represent the time, 10 years (yellow), 20 years (orange) and 30 years (brown) after disturbance.}\label{fig:IDHplot}
\end{figure*}

The functional redundancy was measured as the sum of weighted overlap
among species in the communities. Species functional space were defined
in the main two-dimensional space of a PCA analysis based on all leaf
and stem and maximum height traits (see appendix I for more details).
Plots functoinal redundancy was followed in comparison to their initial
value right after logging so that only communities dynamics are followed
apart from the impact of logging itself. While the functional redundancy
of control plots remained stable along the 30 years it systematically
decreased after disturbance (\ref{fig:RedFun}). The decrease of
functional redundancy was comparable between all disturbed plots but
started later for the most disturbed plots. Plots recovery did not
seemed correlated to the initial disturbance, for five out of nine
disturbed plots the initial functional redundancy was had recovered
while it was still decreasing or stabilized at lower values for the fou
other plots.
